Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
library vs. CLI/GUI toolkit (suggest IPython)
Also address @GaelVaroquaux's comment.

The \sklearn project \citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide efficient and well-established machine learning tools
within a programming environment that is accessible to non-machine learning
experts and reusable in various scientific areas. In itself the project isn't
a novel domain-specific language, but a library that provides machine
learning idioms to a general-purpose high-level language. Among other things,
it includes classical learning algorithms, model selection tools and
preprocessing
procedures. From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the Numpy and
SciPy \citep{vanderwalt2011, varoquaux2013scipy} libraries.
As such, \sklearn is intended to be used within Python scripts
and requires some Python programming knowledge.
At present, it offers no command line or graphical user interface.
% XXX Gael: maybe we should say that it augments a general purpose
% language with machine learning concepts, like numpy augments it with
% array-computing concepts.

>>>>

The \sklearn project \citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide efficient and well-established machine learning tools
within a programming environment that is accessible to non-machine learning
experts and reusable in various scientific areas. In itself the project isn't
a novel domain-specific language, but a library that provides machine
learning idioms to a general-purpose high-level language. Among other things,
it includes classical learning algorithms, model selection tools and
preprocessing procedures.

\sklearn is explicitly a library,
i.e. a collection of classes (in the object-oriented sense)
that users ``import'' into Python scripts/programs.
Use of the package requires basic Python programming knowledge,
and no command-line interface, let alone a GUI,
is offered for non-programmer users.
Instead, interactive use is made possible
by the Python interactive interpreter,
and its enhanced replacement IPython \citep{perez2007ipython},
which offers a \textsc{matlab}-like working environment
specifically designed for scientific use.

From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the NumPy and
SciPy \citep{vanderwalt2011, varoquaux2013scipy} libraries.
Of these, NumPy augments Python with a numeric array datatype
and associated array computing primitives \citep{vanderwalt2011},
while SciPy extends it further
by making common numeric operations available,
either by implementing those in Python/NumPy,
or by wrapping existing C/C{}\verb!++!/Fortran implementations.
In a similar vein, \sklearn extends the general-purpose language Python
with a set of composable machine learning operations.
